---
title: "Usefulness of Forms of Assistance"
editor: visual
execute:
  echo: false
  warning: false
---

```{r}
source("src/functions.R")
loadPackages()
userData<-read_csv("data/anonymizedData.csv")
```

Users were asked how useful they found various forms of assistance.

## Research Help desk

How useful do you find the following forms of assistance? ***Getting assistance at the Research Help desk***

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulResearchHelpDesk", "Research Help desk, All Users", "allUsefulResearchHelpDesk.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulResearchHelpDesk", "Research Help desk,  CAS Users", "casUsefulResearchHelpDesk.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulResearchHelpDesk", "Research Help desk,  GRAD Users", "gradUsefulResearchHelpDesk.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

## Online Chat

How useful do you find the following forms of assistance? ***Getting assistance on chat***

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulChat", "Online Chat, All Users", "allUsefulChat.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulChat", "Online Chat,  CAS Users", "casUsefulChat.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulChat", "Online Chat desk,  GRAD Users", "gradUsefulChat.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::


## Research Consultation

How useful do you find the following forms of assistance? ***Meeting with a librarian in a research consultation***

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulConsultation", "Research Consultation, All Users", "allUsefulConsultation.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulConsultation", "Research Consultation,  CAS Users", "casUsefulConsultation.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulConsultation", "Research Consultation desk,  GRAD Users", "gradUsefulConsultation.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

