---
title: "13. Usefulness of assistance"
editor: visual
execute:
  echo: false
  warning: false
---

***How useful do you find the following forms of assistance?***

```{r}
source("functions.R")
loadPackages()
userData<-read_csv("../data/anonymizedData.csv")
```

### Getting assistance at the Research Help desk

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulResearchHelpDesk", "Research Help desk, All Users", "allUsefulResearchHelpDesk.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulResearchHelpDesk", "Research Help desk,  CAS Users", "casUsefulResearchHelpDesk.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulResearchHelpDesk", "Research Help desk,  GRAD Users", "gradUsefulResearchHelpDesk.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Getting assistance on chat

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulChat", "Online Chat, All Users", "allUsefulChat.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulChat", "Online Chat,  CAS Users", "casUsefulChat.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulChat", "Online Chat,  GRAD Users", "gradUsefulChat.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Meeting with a librarian in a research consultation

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulConsultation", "Research Consultation, All Users", "allUsefulConsultation.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulConsultation", "Research Consultation,  CAS Users", "casUsefulConsultation.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulConsultation", "Research Consultation,  GRAD Users", "gradUsefulConsultation.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Having a librarian meet with my class

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulLibrarianClass", "Librarian Class, All Users", "allUsefulLibrarianClass.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulLibrarianClass", "Librarian Class,  CAS Users", "casUsefulLibrarianClass.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulLibrarianClass", "Librarian Class,  GRAD Users", "gradUsefulLibrarianClass.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Subject and course guides on the library website

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulLibGuide", "Subject / Course Guide, All Users", "allUsefulLibGuide.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulLibGuide", "Subject / Course Guide,  CAS Users", "casUsefulLibGuide.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulLibGuide", "Subject / Course Guide,  GRAD Users", "gradUsefulLibGuide.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Video tutorials on the library website

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulVideoTutorial", "Video Tutorials, All Users", "allUsefulVideoTutorial.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulVideoTutorial", "Video Tutorials,  CAS Users", "casUsefulVideoTutorial.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulVideoTutorial", "Video Tutorials,  GRAD Users", "gradUsefulVideoTutorial.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Other information on the library website

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulLibraryWebsite", "Library Website, All Users", "allUsefulLibraryWebsite.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulLibraryWebsite", "Library Website,  CAS Users", "casUsefulLibraryWebsite.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulLibraryWebsite", "Library Website,  GRAD Users", "gradUsefulLibraryWebsite.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::
