---
title: "4. Frequency of visits"
editor: visual
execute:
  echo: false
  warning: false
---

***How often do you visit the library for the following needs?***

```{r}
source("functions.R")
loadPackages()
userData<-read_csv("../data/anonymizedData.csv")
```

### Studying individually

::: panel-tabset
## All Users

```{r}
frequencyQuestion(userData, "frequencyIndividualStudy", "Individual Study, All Users", "allIndStudy.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
frequencyQuestion(userData, "frequencyIndividualStudy", "Individual Study, CAS Users", "casIndStudy.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
frequencyQuestion(userData, "frequencyIndividualStudy", "Individual Study, GRAD Users", "gradIndStudy.jpg", casOnly=FALSE, gradOnly = TRUE)
```

## On/off campus

```{r}
#frequencyQuestionCampus(userData, "frequencyIndividualStudy", "Individual Study", "indStudyCampus.jpg")


```
:::

### Studying in a group

::: panel-tabset
## All Users

```{r}
frequencyQuestion(userData, "frequencyGroupStudy", "Group Study, All Users", "allGroupStudy.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
frequencyQuestion(userData, "frequencyGroupStudy", "Group Study, CAS Users", "casGroupStudy.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}




frequencyQuestion(userData, "frequencyGroupStudy", "Group Study, GRAD Users", "gradGroupStudy.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Borrowing textbooks from course reserves

::: panel-tabset
## All Users

```{r}
frequencyQuestion(userData, "frequencyCourseReserves", "Course Reserves, All Users", "allCourseReserves.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
frequencyQuestion(userData, "frequencyCourseReserves", "Course Reserves, CAS Users", "casCourseReserves.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}




frequencyQuestion(userData, "frequencyCourseReserves", "Course Reserves, GRAD Users", "gradCourseReserves.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Borrowing or returning books (other than textbooks)

::: panel-tabset
## All Users

```{r}
frequencyQuestion(userData, "frequencyBorrowingBooks", "Borrowing Books, All Users", "allBorrowingBooks.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
frequencyQuestion(userData, "frequencyBorrowingBooks", "Borrowing Books, CAS Users", "casBorrowingBooks.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}




frequencyQuestion(userData, "frequencyBorrowingBooks", "Borrowing Books, GRAD Users", "gradBorrowingBooks.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Getting help from a librarian

::: panel-tabset
## All Users

```{r}
frequencyQuestion(userData, "frequencyGetHelp", "Getting Help, All Users", "allGetHelp.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
frequencyQuestion(userData, "frequencyGetHelp", "Getting Help, CAS Users", "casGetHelp.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}

frequencyQuestion(userData, "frequencyGetHelp", "Getting Help, GRAD Users", "gradGetHelp.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Viewing an exhibit

How often do you visit the library for ***viewing an exhibit***?

::: panel-tabset
## All Users

```{r}
col<-"frequencyExhibit"
lab<-"Viewing Exhibits"
im<-"ViewExhibits"
  
  
frequencyQuestion(userData, col, paste(lab,", All Users"), paste("all",im,".jpg", sep=""), casOnly=FALSE, gradOnly = FALSE)





```

## Undergraduates

```{r}
frequencyQuestion(userData, col, paste(lab, ", CAS Users"), paste("cas",im,".jpg", sep=""), casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}

frequencyQuestion(userData, col, paste(lab,", GRAD Users"), paste("grad",im,".jpg", sep=""), casOnly=FALSE, gradOnly = TRUE)
```
:::

### Printing

::: panel-tabset
## All Users

```{r}
col<-"frequencyPrinting"
lab<-"Printing"
im<-"Printing"
  
  
frequencyQuestion(userData, col, paste(lab,", All Users"), paste("all",im,".jpg", sep=""), casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
frequencyQuestion(userData, col, paste(lab, ", CAS Users"), paste("cas",im,".jpg", sep=""), casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}

frequencyQuestion(userData, col, paste(lab,", GRAD Users"), paste("grad",im,".jpg", sep=""), casOnly=FALSE, gradOnly = TRUE)
```
:::

### Library computers (other than printing)

::: panel-tabset
## All Users

```{r}
col<-"frequencyComputers"
lab<-"Computers"
im<-"Computers"
  
  
frequencyQuestion(userData, col, paste(lab,", All Users"), paste("all",im,".jpg", sep=""), casOnly=FALSE, gradOnly = FALSE)





```

## Undergraduates

```{r}
frequencyQuestion(userData, col, paste(lab, ", CAS Users"), paste("cas",im,".jpg", sep=""), casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}

frequencyQuestion(userData, col, paste(lab,", GRAD Users"), paste("grad",im,".jpg", sep=""), casOnly=FALSE, gradOnly = TRUE)
```
:::

### Getting help from the IT Service Desk

::: panel-tabset
## All Users

```{r}
col<-"frequencyIT"
lab<-"IT"
im<-"IT"
  
  
frequencyQuestion(userData, col, paste(lab,", All Users"), paste("all",im,".jpg", sep=""), casOnly=FALSE, gradOnly = FALSE)




```

## Undergraduates

```{r}
frequencyQuestion(userData, col, paste(lab, ", CAS Users"), paste("cas",im,".jpg", sep=""), casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}

frequencyQuestion(userData, col, paste(lab,", GRAD Users"), paste("grad",im,".jpg", sep=""), casOnly=FALSE, gradOnly = TRUE)
```
:::

## Getting help at the Writing Center

::: panel-tabset
## All Users

```{r}
col<-"frequencyWriting"
lab<-"Writing Center"
im<-"Writing Center"
  
  
frequencyQuestion(userData, col, paste(lab,", All Users"), paste("all",im,".jpg", sep=""), casOnly=FALSE, gradOnly = FALSE)








```

## Undergraduates

```{r}
frequencyQuestion(userData, col, paste(lab, ", CAS Users"), paste("cas",im,".jpg", sep=""), casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}

frequencyQuestion(userData, col, paste(lab,", GRAD Users"), paste("grad",im,".jpg", sep=""), casOnly=FALSE, gradOnly = TRUE)
```
:::
