---
title: "5. Do resources meet your needs"
editor: visual
execute:
  echo: false
  warning: false
---

***Do the following resources meet your needs?***

```{r}
source("functions.R")
loadPackages()
userData<-read_csv("../data/anonymizedData.csv")
```


### Quiet study spaces
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsQuietStudy", "Quiet Study Spaces, All Users", "allNeedsQuietStudy.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsQuietStudy", "Quiet Study Spaces, CAS Users", "casNeedsQuietStudy.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsQuietStudy", "Quiet Study Spaces, GRAD Users", "gradNeedsQuietStudy.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Collaborative study spaces
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsCollabStudy", "Collaborative Study Spaces, All Users", "allNeedsCollabStudy.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsCollabStudy", "Collaborative Study Space, CAS Users", "casNeedsCollabStudy.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsCollabStudy", "Collaborative Study Space, GRAD Users", "gradNeedsQuietStudy.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Reservable study rooms
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsStudyRooms", "Reservable Study Rooms, All Users", "allNeedsStudyRooms.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsStudyRooms", "Reservable Study Rooms, CAS Users", "casNeedsStudyRooms.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsStudyRooms", "Reservable Study Rooms, GRAD Users", "gradNeedsStudyRooms.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Textbooks from course reserves
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsTextbooks", "Textbooks from Course Reserves, All Users", "allNeedsTextbooks.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsTextbooks", "Textbooks from Course Reserves, CAS Users", "casNeedsTextbooks.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsTextbooks", "Textbooks from Course Reserves, GRAD Users", "gradNeedsTextbooks.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Summit borrowing
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsSummit", "Summit Borrowing, All Users", "allNeedsSummit.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsSummit", "Summit Borrowing, CAS Users", "casNeedsSummit.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsSummit", "Summit Borrowing, GRAD Users", "gradNeedsSummit.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Interlibrary loan
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsIll", "Interlibrary Loan, All Users", "allNeedsIll.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsIll", "Interlibrary Loan, CAS Users", "casNeedsIll.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsIll", "Interlibrary Loan, GRAD Users", "gradNeedsIll.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Library printers
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsPrinters", "Library printers, All Users", "allNeedsPrinters.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsPrinters", "Library printers, CAS Users", "casNeedsPrinters.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsPrinters", "Library printers, GRAD Users", "gradNeedsPrinters.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Library computers
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsComputers", "Library computers, All Users", "allNeedsComputers.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsComputers", "Library computers, CAS Users", "casNeedsComputers.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsComputers", "Library computers, GRAD Users", "gradNeedsComputers.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### Library scanners
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsScanners", "Library scanners, All Users", "allNeedsScanners.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsScanners", "Library scanners, CAS Users", "casNeedsScanners.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsScanners", "Library scanners, GRAD Users", "gradNeedsScanners.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

### AV/tech borrowing (headphones, laptops, etc.)
::: panel-tabset
## All Users

```{r}
needsQuestion(userData, "needsTechBorrowing", "AV/tech borrowing, All Users", "allNeedsTechBorrowing.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
needsQuestion(userData, "needsTechBorrowing", "AV/tech borrowing, CAS Users", "casNeedsTechBorrowing.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
needsQuestion(userData, "needsTechBorrowing", "AV/tech borrowing, GRAD Users", "gradNeedsTechBorrowing.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::
