---
title: "8. Usefulness of tools"
editor: visual
execute:
  echo: false
  warning: false
---

```{r}
source("functions.R")
loadPackages()
userData<-read_csv("../data/anonymizedData.csv")
```

***8. When starting a research project, how useful do you find the following tools?***

## Primo Catalog

When starting a research project, how useful do you find the following tools? \***Primo (the library catalog)**

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulPrimo", "Primo, All Users", "allUsefulPrimo.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulPrimo", "Primo,  CAS Users", "casUsefulPrimo.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulPrimo", "Primo, GRAD Users", "gradusefulPrimo.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

## Library databases other than Primo

When starting a research project, how useful do you find the following tools? ***Library databases other than Primo (e.g. JSTOR, EBSCO)***

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulDatabases", "Library Databases, All Users", "allUsefulDatabases.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulDatabases", "Library Databases,  CAS Users", "casUsefulDatabases.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulDatabases", "Library Databases, GRAD Users", "gradusefulDatabases.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

## Google

When starting a research project, how useful do you find the following tools? ***Google***

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulGoogle", "Google, All Users", "allUsefulGoogle.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulGoogle", "Google,  CAS Users", "casUsefulGoogle.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulGoogle", "Google, GRAD Users", "gradusefulGoogle.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::

## Google Scholar

When starting a research project, how useful do you find the following tools? ***Google Scholar***

::: panel-tabset
## All Users

```{r}
usefulQuestion(userData, "usefulGoogleScholar", "Google Scholar, All Users", "allUsefulGoogleScholar.jpg", casOnly=FALSE, gradOnly = FALSE)

```

## Undergraduates

```{r}
usefulQuestion(userData, "usefulGoogleScholar", "Google Scholar,  CAS Users", "casUsefulGoogleScholar.jpg", casOnly=TRUE, gradOnly = FALSE)
```

## Graduates

```{r}
usefulQuestion(userData, "usefulGoogleScholar", "Google Scholar, GRAD Users", "gradusefulGoogleScholar.jpg", casOnly=FALSE, gradOnly = TRUE)
```
:::
